---
title: "SAPD Faction Report"
fontsize: 20
output:
  word_document:
    fig_caption: no

---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, dpi = 300)

```


<Div custom-style = "Publication subtitle">  </Div>
Extract date: `r format(Sys.Date(), '%d %B %Y')`    
Contact: [Bennyy](mailto:harleyb101010@gmail.com)   

## Background

This is the IMRP's activity report which is based on faction rosters across the entire community. This report is generic and can be used for every faction.

## Figure 1: Number of members in SAPD

This is total number of members in SAPD based on roster date

```{r graph_user, ft.align="left", fig.width=7, fig.height=4}
full_member_graph
```

## Figure 2: Number of members by tier

This is total number of members by tier in SAPD based on roster date

```{r graph_2, ft.align="left", fig.width=7, fig.height=4}
member_count_tier_graph
```

## Table 1: Number of members by tier based on `r format(Sys.Date(), '%d %B %Y')` staff roster
```{r table_tier, ft.align="center", fig.width=7, fig.height=4}
Tier_List_Output

```

## Figure 3: Number of members by activity critera

```{r graph_activity, ft.align="center", fig.width=7, fig.height=4}
activity_graph

```

## Figure 4: Tier 0 Breakdown based on activity

```{r graph_activity_tier0, ft.align="center", fig.width=7, fig.height=4}

activity_graph_tier_0
```


## Figure 4: Tier 1 Breakdown based on activity

```{r graph_activity_tier1, ft.align="center", fig.width=7, fig.height=4}

activity_graph_tier_1
```

## Figure 5: Tier 2 Breakdown based on activity

```{r graph_activity_tier2, ft.align="center", fig.width=7, fig.height=4}

activity_graph_tier_2
```


## Figure 6: Tier 3 Breakdown based on activity

```{r graph_activity_tier3, ft.align="center", fig.width=7, fig.height=4}

activity_graph_tier_3
```

## Figure 7: Inactives Breakdown based on tier

```{r inactive_graph, ft.align="center", fig.width=7, fig.height=4}

inactive_graph
```